\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-10-03 NAR_DRAFT.tex
add citation for calibration

The improved calibration of \batcave posterior probabilities compared to MuTect provides several advantages.
In practice, called variants are often manually reviewed to further reduce false positives \cite{Barnell2019}.
Improved calibration enables users to focus review on the most questionable variants.
In the clinic, identified variants act as biomarkers for susceptibility to targeted drugs \cite{Boutros2015a}.
%Well-calibrated posterior probabilities facilitate the use of probabilistic risk models in the choice of treatment \cite{XXX}, rather than an all or nothing approach.
For research purposes, the International Cancer Genome Consortium recommends that catalogs of somatic mutations target a precision of 95\% and a recall of 80\% \cite{Icgc}.
Achieving this goal while minimizing cost demands well-calibrated posterior probabilities.

@@

The \texttt{batcaver} R package can be downloaded or installed from \texttt{github.com/bmannakee/batcaver}
The version of \texttt{batcaver} used to generate results, and all analysis code have been preserved on Zenodo \texttt{https://doi.org/10.5281/zenodo.3471715}
Python code used to generate simulated tumors has been preserved on Zenodo \texttt{https://doi.org/10.5281/zenodo.3471741}

>>>>

The improved calibration of \batcave posterior probabilities compared to MuTect provides several advantages.
In practice, called variants are often manually reviewed to further reduce false positives \cite{Barnell2019}.
Improved calibration enables users to focus review on the most questionable variants.
In the clinic, identified variants act as biomarkers for susceptibility to targeted drugs \cite{Boutros2015a}.
Well-calibrated posterior probabilities facilitate the use of probabilistic risk models in the choice of treatment \cite{Holmberg2013}, rather than an all or nothing approach.
For research purposes, the International Cancer Genome Consortium recommends that catalogs of somatic mutations target a precision of 95\% and a recall of 80\% \cite{Icgc}.
Achieving this goal while minimizing cost demands well-calibrated posterior probabilities.

@@

The \texttt{batcaver} R package can be downloaded or installed from \texttt{http://github.com/bmannakee/batcaver}
The version of \texttt{batcaver} used to generate results, and all analysis code have been preserved on Zenodo \texttt{https://doi.org/10.5281/zenodo.3471715}
Python code used to generate simulated tumors has been preserved on Zenodo \texttt{https://doi.org/10.5281/zenodo.3471741}
